Finiteness in Cubical Type Theory

### 2020-01-13 paper.tex
new abstract

\input{preamble}
\title{Finiteness and Cardinality in Homotopy Type Theory}
\author{Donnacha Oisín Kidney}
\authorrunning{D. O. Kidney}
\institute{University College Cork \and
  \email{o.kidney@cs.ucc.ie}}
\begin{document}
\maketitle
\begin{abstract}
  We study finiteness in Homotopy Type Theory, classifying five fundamentally
  different finiteness predicates and proving formally the relationship between
  them.
  We also prove the closure properties of each predicate, which includes a proof
  that decidable Kuratowski finite sets form a topos.

>>>>

\input{preamble}
\title{Finiteness in Cubical Type Theory}
\author{Donnacha Oisín Kidney}
\authorrunning{D. O. Kidney}
\institute{University College Cork \and
  \email{o.kidney@cs.ucc.ie}}
\begin{document}
\maketitle
\begin{abstract}
  We study five different notions of finiteness in Cubical Type Theory and prove
  the relationship between them.
  In particular we show that any totally ordered Kuratowski finite type is
  manifestly Bishop finite.

  We also prove closure properties for each finite type, and classify them
  topos-theoretically.
  For instance we show that the category of decidable Kuratowski finite sets
  (also called the category of cardinal finite sets) form a \(\Pi\)-pretopos.
